    \documentclass[10pt, letterpaper]{article}
    
    \usepackage[top=1.2cm, bottom=1.8cm, left=1.8cm, right=1.8cm]{geometry}
    \usepackage{titlesec}
    \usepackage{enumitem}
    \usepackage[hidelinks]{hyperref}
    \usepackage{iftex}
    \ifPDFTeX
      \input{glyphtounicode}
      \pdfgentounicode=1
      \usepackage[T1]{fontenc}
      \usepackage[utf8]{inputenc}
      \usepackage{lmodern}
    \fi
    \pagestyle{empty}
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{3pt}
    \renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}
    \titleformat{\section}{\bfseries\large}{}{0pt}{}[\titlerule]
    \titlespacing{\section}{0pt}{4pt}{3pt}
    
    \begin{document}
    
    \begin{center}
      {\LARGE \textbf{DATTA SAI V V N}} \\
      Chicago, IL \,|\, +1-872-899-7710 \,|\, \href{mailto:dattasaivvn@gmail.com}{dattasaivvn@gmail.com} \,|\, \href{https://www.linkedin.com/in/dvvn}{https://www.linkedin.com/in/dvvn}
    \end{center}













    
\section*{Summary}
\textbf{Data Science Engineer and MSCS UIC Graduate with 3 years of combined experience in machine learning, software, and research.}  
Skilled in statistical modeling, segmentation, regression, and time-series forecasting using Python, SQL, Spark, and Tableau for business insights.  
Combines analytical rigor with production-level ML deployment expertise to drive scalable, data-driven decision-making and customer growth.  

















    \section{Education}
    \textbf{University of Illinois Chicago}, Chicago, USA \hfill Aug 2024 -- May 2026 \\
    Master of Science in Computer Science \\
    Relevant Coursework: Data Science, AI Engineering, Network Communication, System Engineering, Machine Learning
            



















\section{Skills}
\textbf{Programming Languages \& Tools:} Python, SQL, R, Pandas, NumPy, Git, Jupyter, VS Code, Linux \\ 
\textbf{ML:} Scikit-learn, XGBoost, LightGBM, Regression, Clustering, Time Series Forecasting \\ 
\textbf{DL and NLP:} PyTorch, TensorFlow, Keras, BERT, spaCy, Sequence Modeling \\ 
\textbf{Data Visualization:} Tableau, Power BI, Matplotlib, Seaborn, KPI Dashboards, Data Storytelling \\ 
\textbf{Data Engineering \& Databases:} Spark, Hive, Hadoop, PostgreSQL, MySQL, Airflow \\ 
\textbf{MLOps:} MLflow, Docker, FastAPI, AWS (S3, Glue, SageMaker), Azure ML, CI/CD  























    
    
\section{Experience}

\textbf{System Engineer} \hfill Aug 2022 -- Aug 2024 \\
\textit{Alstom Transportation, Bangalore, India}\vspace{-0.2em}
\begin{itemize}[leftmargin=*, topsep=0pt, itemsep=0pt, parsep=0pt, partopsep=0pt]
  \item Built ML and OCR pipeline to extract and classify requirements from customer documents using Python and NLP.  
  \item Engineered features and trained models with Scikit-learn and PyTorch to improve accuracy and reliability.  
  \item Deployed FastAPI-based inference service on AWS for real-time requirement classification and allocation.  
  \item Automated reporting and traceability dashboards in Power BI to monitor model performance and compliance.  
\end{itemize}
\vspace{0.1cm}
\textbf{Research Intern -- Machine Learning } \hfill Jun 2022 -- Aug 2022 \\
\textit{Indian Institute of Technology Ropar, India}\vspace{-0.2em}
\begin{itemize}[leftmargin=*, topsep=0pt, itemsep=0pt, parsep=0pt, partopsep=0pt]
  \item Preprocessed and analyzed research datasets using Python, Pandas, and NumPy for ML pipeline development.  
  \item Implemented supervised and unsupervised learning models including XGBoost, SVMs, and clustering algorithms.  
  \item Validated models with cross-validation and visualized results using Matplotlib and Seaborn for reproducibility.  
\end{itemize}
\vspace{0.1cm}
\textbf{Data Science Intern} \hfill Jan 2022 -- Jun 2022 \\
\textit{Ernst \& Young, Chennai, India}\vspace{-0.2em}
\begin{itemize}[leftmargin=*, topsep=0pt, itemsep=0pt, parsep=0pt, partopsep=0pt]
  \item Built predictive models using Regression and Decision Tree algorithms to forecast IT service response time.  
  \item Automated data collection and preprocessing pipelines with Python, Pandas, and SQL for analytics reporting.  
  \item Deployed ML workflow on ServiceNow data to identify process bottlenecks and improve efficiency metrics.  
  \item Visualized model outcomes and KPIs using Power BI dashboards for data-driven decision-making by leadership.  
\end{itemize}


























\section{Projects}

\textbf{B2B Customer Journey Analytics Platform} | \textit{Python, SQL, Spark, Tableau, Airflow, AWS} \\ 
\vspace{-0.45cm}
\begin{itemize}[leftmargin=*, topsep=0pt, itemsep=0pt, parsep=0pt, partopsep=0pt]
  \item Built end-to-end data pipelines for analyzing multi-channel B2B customer journeys and engagement.  
  \item Applied clustering and regression to uncover retention drivers and optimize customer touchpoints.  
  \item Enabled actionable insights via Tableau dashboards, improving conversion and retention metrics by 20\%.  
\end{itemize}

\vspace{0.15cm}
\textbf{Propensity and Segmentation Modeling System} | \textit{Python, Scikit-learn, LightGBM, SQL, Power BI, Airflow} \\ 
\vspace{-0.45cm}
\begin{itemize}[leftmargin=*, topsep=0pt, itemsep=0pt, parsep=0pt, partopsep=0pt]
  \item Developed customer propensity and segmentation models using behavioral and transactional datasets.  
  \item Automated ETL workflows and performance tracking pipelines for model retraining and reporting.  
  \item Improved lead prioritization accuracy by 22\%, driving proactive B2B customer engagement programs.  
\end{itemize}

\vspace{0.15cm}
\textbf{Demand Forecasting \& KPI Intelligence Dashboard} | \textit{Python, XGBoost, Spark, Tableau, AWS Glue} \\ 
\vspace{-0.45cm}
\begin{itemize}[leftmargin=*, topsep=0pt, itemsep=0pt, parsep=0pt, partopsep=0pt]
  \item Engineered time-series forecasting models for predicting product demand and campaign outcomes.  
  \item Designed KPI dashboards integrating real-time metrics from multiple business sources.  
  \item Achieved 15\% forecast error reduction, enhancing business planning and growth optimization.  
\end{itemize}



    





    
    
    
    \end{document}
    